---
title: "Discover admiral Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Discover admiral Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#### Variable Listing

Use the table below to identify ADaM variables and the {admiral} functions that derive them.

```{r echo=FALSE}
admiraldiscovery::interactive_discovery("reactable")
```

#### Missing Variables

If you notice an ADaM variable that is missing, please [file an issue on GitHub](https://github.com/pharmaverse/admiraldiscovery/issues) to have it added.

#### Deprecated/Superseded

<span style="background-color: #ffb3ba">Deprecated</span> and <span style="background-color: #ffffba">Superseded</span> functions are highlighted according to their statuses in `r admiraldiscovery::admiral_pkg_versions()`.
If you see a deprecated or superseded function, please file an issue on GitHub for the respective admiral package so the table can be updated.

The links to template examples are the most recent available.
To access a template from your installed version of a package, use the `admiral::use_ad_template()` function.
